---
title: "Theme Gallery"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Theme Gallery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 9,
  fig.height = 6,
  dpi = 150
)
```

## Theme Gallery

This vignette showcases all 7 built-in themes using the Political Democracy
SEM model from lavaan.

```{r model, eval = FALSE}
library(lavaan)
library(ggsemplot)

sem_model <- '
  ind60 =~ x1 + x2 + x3
  dem60 =~ y1 + y2 + y3 + y4
  dem65 =~ y5 + y6 + y7 + y8
  dem60 ~ ind60
  dem65 ~ ind60 + dem60
'

fit <- sem(sem_model, data = PoliticalDemocracy)
```

### Classic (default)
Clean black-and-white academic style. Suitable for most journal submissions.

```{r classic, eval = FALSE}
plot_sem(fit, layout = "tree2", theme = "classic",
         title = "Classic Theme")
```

### Modern
Soft color palette with rounded corners. Contemporary look for presentations.

```{r modern, eval = FALSE}
plot_sem(fit, layout = "tree2", theme = "modern",
         title = "Modern Theme")
```

### APA
Strict APA format. Black lines, no fills, serif font. Ideal for psychology journals.

```{r apa, eval = FALSE}
plot_sem(fit, layout = "tree2", theme = "apa",
         title = "APA Theme")
```

### Minimal
Ultra-clean design with thin lines and generous whitespace.

```{r minimal, eval = FALSE}
plot_sem(fit, layout = "tree2", theme = "minimal",
         title = "Minimal Theme")
```

### Nature
Inspired by Nature/Science journal figures. Muted blue-grey tones.

```{r nature, eval = FALSE}
plot_sem(fit, layout = "tree2", theme = "nature",
         title = "Nature Theme")
```

### Dark
Dark background optimized for slides and presentations.

```{r dark, eval = FALSE}
plot_sem(fit, layout = "tree2", theme = "dark",
         title = "Dark Theme")
```

### Colorful
Vibrant, high-saturation colors for posters and eye-catching presentations.

```{r colorful, eval = FALSE}
plot_sem(fit, layout = "tree2", theme = "colorful",
         title = "Colorful Theme")
```

## Color Palettes

Beyond themes, you can apply color palettes to any theme:

```{r palettes, eval = FALSE}
plot_sem(fit, theme = "classic") + scale_sem_palette("ocean")
plot_sem(fit, theme = "classic") + scale_sem_palette("earth")
plot_sem(fit, theme = "classic") + scale_sem_palette("pastel")
plot_sem(fit, theme = "classic") + scale_sem_palette("viridis")
plot_sem(fit, theme = "classic") + scale_sem_palette("grey")
```
